\def\dMon{Mon, 03/08}
\def\dTues{Tues, 03/09}
\def\dWed{Wed, 03/10}
\def\dThur{Thur, 03/11}
\def\dFri{Fri, 03/12}
\def\dSat{Sat, 03/13}
\def\dSun{Sun, 03/14}
\placeDate

\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
	\item \itemHead{Reading \& Presentation}[Videogame Music][Response Due \dMon]
	      \begin{itemize}
		      \item \emph{Section 2: Video-game Music} from \href{supplements/Music_Sound_and_Multimedia_-_From_the_Live_to_the_Virtual_(Music_and_the_Moving_Image)_(2008).pdf}{Music, Sound and Multimedia}
	      \end{itemize}

	\item \itemHead{Exercise}[Project Progress Report][Due \dSun] \newline
	      Submit appropriate documents (videos, images, audio, etc.) that clearly demonstrate the progress you have made during the past week. Upload your file(s), video links, shared documents, etc. to \discordE
	\item \itemHead{Sample Library}[Additions][Due \dSun] \newline
	      Submit a minimum of 2 additional field recordings to the \href{\samplelibPermURL}{sample library}.
	      \begin{itemize}
		      \item \textbf{Filename:} \texttt{[TYPE] Recording CLEAN (Firstname Lastname)}
		      \item \textbf{Specs:} 24bit 44100hz WAV File
		      \item \textbf{Track Submission:} Submit your file names to \discordS
	      \end{itemize}
	\item \itemHead{Screening}[Making Waves][Response Due \dWed]
	      \begin{itemize}
		      \item \href{https://www.youtube.com/watch?v=xsckp8r1-8c}{\emph{Making Waves: The Art of Cinematic Sound}} (2019), Midge Costin
		      \item \textbf{Prompt:} How does technological innovation inspire art or vice versa? How would you best describe the creative collaboration process between directors and their sound artists? How does sound contribute to a form of storytelling? How does cinematic sound change our perception of the unknown? Describe three sound-related processes detailed in the film. What is something you learned from the film today that you found particularly interesting? Submit your response to \discord{Discussions}{making-waves}
	      \end{itemize}
\end{itemize}